\MakeUppercase{Linear versus centred Colouring Numbers}\thanks{This research was partly funded by NSERC.}

### 2021-10-06 lin-vs-cen.tex
Small fix

  Conditions~(\ref{never_far}) and (\ref{three_in_ball}) of \cref{voronoi_mapping} imply that each any ball of radius $\min\{\beta/8-1, \beta/12\}/2$ contains at most three elements of $R$.  This condition is satisfied for $\beta= 12\cdot18 = 218$ (so the conditions on $\alpha$ are satisified for any $\alpha = r(7\beta/2+1)^2=2331729r$).  Therefore, by \cref{one_path_enchilada}, there exists a path $P$ in $G^{\onesub}_k$ that contains every vertex of $R$, that goes straight at every straight vertex of $R$ and that bends at every bent vertex of $R$. These latter two conditions guarantee that $V(P)$ contains $P_x$ for each $x\in R$. For each colour $c\in\{1,\ldots,C\}$, there are at least two vertices $x_c,y_c\in R$ such that $P_{x_c}$ and $P_{y_c}$ each contain some vertex of colour $c$.  Therefore the path $P$ contains two vertices of each colour, so $P$ has no center and therefore $\varphi$ is not a linear colouring of $H$.  Since $\varphi$ is an arbitrary $\epsilon k$-colouring of $H$, this implies that $\chilin(H)\ge \epsilon k = \Theta(k/\alpha)=\Theta(k/r)$.
\end{proof}

>>>>

  Conditions~(\ref{never_far}) and (\ref{three_in_ball}) of \cref{voronoi_mapping} imply that each any ball of radius $\min\{\beta/8-1, \beta/12\}/2$ contains at most three elements of $R$.  Setting $\beta= 12\cdot2\cdot18 = 436$ (so the conditions on $\alpha$ are satisified for $\alpha = r(7\beta/2+1)^2=2331729r$) gives a point set $R$ that satisfies the requirements for \cref{one_path_enchilada}.  Therefore, by \cref{one_path_enchilada}, there exists a path $P$ in $G^{\onesub}_k$ that contains every vertex of $R$, that goes straight at every straight vertex of $R$ and that bends at every bent vertex of $R$. These latter two conditions guarantee that $V(P)$ contains $P_x$ for each $x\in R$. For each colour $c\in\{1,\ldots,C\}$, there are at least two vertices $x_c,y_c\in R$ such that $P_{x_c}$ and $P_{y_c}$ each contain some vertex of colour $c$.  Therefore the path $P$ contains two vertices of each colour, so $P$ has no center and therefore $\varphi$ is not a linear colouring of $H$.  Since $\varphi$ is an arbitrary $\epsilon k$-colouring of $H$, this implies that $\chilin(H)\ge \epsilon k = \Theta(k/\alpha)=\Theta(k/r)$.
\end{proof}
